\documentclass{article}
\usepackage[margin=1in]{geometry}


\begin{document}

\title{\textbf{Comparable UAS Designs}}
\author{OpenUAS Team}
\maketitle

This document lists the specifications of other current Small Unmanned Aircraft Systems (SUAS).

\section{RQ-14A Dragon Eye}

This UAV was created by the Naval Research Laboratory and the Marine Corps Warfighting Laboratory. The Dragon Eye is used by the United States Marine Corps.\\\\
\textbf{Wingspan:} 3.75 ft\\
\textbf{Weight:} 5.9 lb\\
\textbf{Payload:} \\
\textbf{Length:} 3.0 ft\\
\textbf{Height:} 11 in\\
\textbf{Launch Method:} Hand or bungee\\
\textbf{Materials:} Carbon fiber, plastic, aluminum, copper, rubber, styrofoam\\
\textbf{Power Plant:} Two battery powered motors\\
\textbf{Fly Time:} Approx. 1 hr\\

\textbf{Source:} Smithsonian National Air and Space Museum

\section{Razor}

This UAV was created by the University of Virginia for the Department of Defense. The Razor has a flying wing design.\\\\
\textbf{Wingspan:} 4 ft\\
\textbf{Weight:} 6 lb\\
\textbf{Payload:} Up to 1.5 lb\\
\textbf{Length:} \\
\textbf{Height:}\\
\textbf{Launch Method:} Hand or bungee\\
\textbf{Materials:} 3-D printed plastic\\
\textbf{Power Plant:} \\
\textbf{Fly Time:} Approx. 45 min\\

\textbf{Sources:} University of Virginia Link Lab, Additive Manufacturing

\section{FQM-151A Pointer}

This UAV was created by AeroVironment Inc. and is used by the Army and the Marine Corps. This is an older system, first used by the military in 1990. It is still in use today, however, this UAV is being replaced by other models.\\\\
\textbf{Wingspan:} 9 ft\\
\textbf{Weight:} 9.6 lb\\
\textbf{Payload:} \\
\textbf{Length:} 6 ft \\
\textbf{Height:}\\
\textbf{Launch Method:} Hand\\
\textbf{Materials:} \\
\textbf{Power Plant:} One battery (lithium) powered motor\\
\textbf{Fly Time:} Approx. 1 hr\\

\textbf{Sources:} Designation Systems, Wikipedia

\section{RQ-11B Raven}

This UAV was created by AeroVironment Inc. and is used by the United States Military.\\\\
\textbf{Wingspan:} 4.5 ft\\
\textbf{Weight:} 4.2 lb\\
\textbf{Payload:} 6.5 oz\\
\textbf{Length:} 3 ft \\
\textbf{Height:}\\
\textbf{Launch Method:} Hand\\
\textbf{Materials:} \\
\textbf{Power Plant:} One electric motor using rechargable lithium ion batteries\\
\textbf{Fly Time:} Approx. 1 to 1.5 hr\\

\textbf{Source:} AeroVironment


\section{Parrot Disco FPV}
This is a commercial UAV created by Parrot.\\\\
\textbf{Wingspan:} 3.75 ft\\
\textbf{Weight:} 1.65 lb\\
\textbf{Payload:} \\
\textbf{Length:}  \\
\textbf{Height:}\\
\textbf{Launch Method:} Hand\\
\textbf{Materials:} Plastic foam \\
\textbf{Power Plant:} \\
\textbf{Fly Time:} Approx. 45 mins\\

\textbf{Sources:} Parrot, CNET


\end{document}