\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Albatross Video Findings}
\date{November 2018}

\begin{document}

\maketitle

\section*{Build Video}
\begin{description}
  \item[$\bullet$] 1412 folding prop
  \item[$\bullet$] Caps for servos are pretty bad or can be. 5065 servos
  \item[$\bullet$] All servos are gooped in. It doesn’t crack and takes impact well.
  \item[$\bullet$] Twisted wire is better than flat wire because the power may spike causing interference.
  \item[$\bullet$] Angle servo arms in the flat, so they don’t have to work as hard to keep the flap neutral.
  \item[$\bullet$] Vector flight controller
  \item[$\bullet$] There is a left and right side to pretty much everything.
  \item[$\bullet$] Label the tops of everything for convenience.
  \item[$\bullet$] Two 3S 8000 batteries in series.
  \item[$\bullet$] Prop will be close to ground on rotation.
\end{description}

\section*{Flight Video}
\begin{description}
  \item[$\bullet$] A few degrees of camber, Holding down elevator 2/3 throttle
  \item[$\bullet$] Neutral elevator, it lifts off on its own.
  \item[$\bullet$] Castel EDGE 100 shuts down due to over-amp at 150A cutoff.
  \item[$\bullet$] Has constant camber, so it climbs quickly.
  \item[$\bullet$] Starting landing pattern keeping flaps on with power at 1/2.
\end{description}
It will most likely pull more than 150 amps on takeoff and shut off the ESC, but it will come back online quickly and then you shouldn't have a problem. He had to move his CG slightly ahead of where the spec told him to put it. We may want to think about reinforcing the belly due to its small area.

\end{document}
